---
title: "Do You Have a Hot Name, Baby?"
assignment: "SDS-192, Mini-Project 1"
author: "Jay-Ho Chung"
date: "2/18/2018"
output: 
  html_document: 
    code_folding: hide
    df_print: paged
    theme: spacelab
---
# Introduction
  The graphics use the `babynames` dataset from the Social Security Administration. The dataset has five variables. The `year`, `sex`, `name`, `n`, and `prop` variables represent the specific year (1880 to 2015), the gender of an applicant (`M` or `F`), the number of applicants born with a certain name, and the ratio of the number of people with a name, `n`, to the total number of applicants of the same gender in that same year. 

  The graphics illustrate the trends of the most popular male and female name in 1955, 1970, 1985, 2000, and 2015. For males, Michael was the most popular name in 1955, 1970, and 1985. It retained its popularity in 2000 and 2015, although Jacob and Noah were the most popular names in those years. For females, one specific name was not popular for a long time. Names that were popular in one 15-year interval were not as popular later.

  The key assigns a distinct *color* to each name to separate the categorical variable of `name`. The plot uses the `geom_line` and `geom_point` for the geometric mapping. The *direction* of the line illustrates the change in the popularity of a name. The *size* of the line shows the lines. The points clarify that a name is the most popular in each of the four 15-year intervals. The visual cue of *color* separates each line’s associated name. The variable of `year` was placed on the horizontal axis and `prop` on the vertical axis to show the change in the proportion of people with a name on a linear scale. `prop` was mapped instead of `n` because `n` varied every year most likely from birth rates. The *Cartesian* coordinate system shows the change in the `prop` with `year`. Context is provided by the axes, title, and key.



# The Code

## Packages
```{r setup, include = TRUE , message = FALSE}
library(babynames) # Loading our dataset, babynames
library(tidyverse) # Loading tidyverse to use ggplot
library(ggthemes) # Loading ggthemes
library(gridExtra) # Loads the gridExtra pacakge
```

## Finding the Most Popular Female Names in 1955, 1970, 1985, 2000, and 2015
```{r , include = TRUE}
# Chose 15-year intervals b/c there was less of a change per 5 or 10 years

f55 <- babynames %>% # Piping out the babynames data into "f55"
   arrange(desc(n)) %>% # Arranges the data from top to bottom
   filter(year == 1955 , sex == "F") %>% # Specifies the year, 1955, and gender, female, that we want to look at
   head(1) #Shows the top result of the most popular female name in 1955


f70 <- babynames %>% # Piping out the babynames data into "f70"
  arrange(desc(n)) %>% # Arranges the data from top to bottom
  filter(year==1970, sex == "F") %>% # Specifies the year, 1970, and gender, female, that we want to look at
  head(1) #Shows the top result of the most popular female name in 1970

f85 <- babynames %>% # Piping out the babynames data into "f85"
  arrange(desc(n)) %>% # Arranges the data from top to bottom
  filter(year == 1985 , sex == "F") %>% # Specifies the year, 1985, and gender, female, that we want to look at
  head(1) #Shows the top result of the most popular female name in 1985

f00 <- babynames %>% # Piping out the babynames data into "f00"
  arrange(desc(n)) %>% # Arranges the data from top to bottom
  filter(year == 2000 , sex == "F") %>% # Specifies the year, 2000, and gender, female, that we want to look at
  head(1) #Shows the top result of the most popular female name in 2000
  
f15 <- babynames %>% # Piping out the babynames data into "f15"
  arrange(desc(n)) %>% # Arranges the data from top to bottom
  filter(year == 2015 , sex == "F") %>% # Specifies the year, 2015, and gender, female, that we want to look at
  head(1) #Shows the top result of the most popular female name in 2015
```

```{r , include = TRUE , results = "hide"}
# Calling on the functions for female names to see what we can tell
f55 # (1955): Mary is the most popular name
f70 # (1970): Jennifer is the most popular name
f85 # (1985): Jessica is the most popular name
f00 # (2000): Emily is the most popular name
f15 # (2015): Emma is the most popular name
```

```{r, include = TRUE}

mary <- babynames %>% # Taking the most popular name from 1955 and putting in a dataset
  filter(name == "Mary" , year >= 1955 , sex == "F") # Filter the name here. Start at 1955 for all to see how these names have changed in popularity over time

jennifer <- babynames %>% # Taking the most popular name from 1970 and putting in a dataset
  filter(name == "Jennifer" , year >= 1955 , sex == "F")

jessica <- babynames %>% # Taking the most popular name from 1985 and putting in a dataset
  filter(name == "Jessica" , year >= 1955 , sex == "F")

emily <- babynames %>% # Taking the most popular name from 2000 and putting in a dataset
  filter(name == "Emily" , year >= 1955 , sex == "F")

emma <- babynames %>% # Taking the most popular name from 2-15 and putting in a dataset
  filter(name == "Emma" , year >= 1955 , sex == "F")
```

## Finding the Most Popular Male Names in 1955, 1970, 1985, 2000, and 2015
```{r , include = TRUE}
# So these filter out the most popular male names from the year from 1955 to 2015 in 15 year intervals
m55 <- babynames %>% #Piping the babynames data into "m55"
  arrange(desc(n))%>% # Arranging in desc(n) to see the names from top to bottom
  filter(year == 1955 , sex == "M") %>% # Taking the specific data from 1955
  head(1) # Showing the top name in our specific year

m70 <- babynames %>% #Piping the babynames data into "m70"
  arrange(desc(n))%>% # Arranging in desc(n) to see the names from top to bottom
  filter(year == 1970 , sex == "M") %>% # Taking the specific data from 1955
  head(1) # Showing the top name in our specific year

m85 <- babynames %>% #Piping the babynames data into "m85"
  arrange(desc(n))%>% # Arranging in desc(n) to see the names from top to bottom
  filter(year == 1985 , sex == "M") %>% # Taking the specific data from 1955
  head(1) # Showing the top name in our specific year

m00 <- babynames %>% #Piping the babynames data into "m00"
  arrange(desc(n))%>% # Arranging in desc(n) to see the names from top to bottom
  filter(year == 2000 , sex == "M") %>% # Taking the specific data from 2000
  head(1) # Showing the top name in our specific year

m15 <- babynames %>% #Piping the babynames data into "m15"
  arrange(desc(n))%>% # Arranging in desc(n) to see the names from top to bottom
  filter(year == 1955 , sex == "M") %>% # Taking the specific data from 2015
  head(1) # Showing the top name in our specific year
```

```{r , results = "hide" , include = TRUE}
# Here, we call up on what we just made to see the results of the most popular names in 1955, 1970, 1985, 2000, and 2015.
# We need to call upon these if we want to see them
m55
m70
m85
m00
m15
# From this, we can identify the most popular names from each 15-year interval
# 1955: Most popular male name is Michael
# 1970: Michael
# 1985: Michael
# 2000: Jacob
# 2015: Noah
```

```{r}
# Filers each of the most popular names, starting at 1955,into data
noah <- babynames %>% # 
  filter(name == "Noah", year >= 1955, sex == "M") # filters the dataset to only include males with the name Noah-- the most popular name in 2015, from 1955


jacob <- babynames %>% #Jacob is the most popular name from 2000
  filter(name=="Jacob", year>= 1955, sex=="M") # filters the dataset to only include males with the name Jacob-- the most popular name in 2000 -- from 1955

michael  <- babynames %>% 
  filter(name == "Michael", year >= 1955, sex == "M") # Michael is the most popular name in 1955, 1970, and 1985
```

# Plotting 

## The Graphics
```{r}
agg_m <- ggplot() + # ggplot() lets us graph all of this
  geom_line(data = noah , aes(x = year, y = prop, color = name) , size = 1) + # Plotting the data called "noah" to see how the name "Noah" has changed over the years
  geom_line(data = michael , aes(x = year, y = prop, color = name) , size = 1) + # Same here
  geom_line(data = jacob , aes(x = year, y = prop, color = name) , size = 1) + # And here
  geom_point(aes(x = 1955 , y = .0423)) + # As mentioned in the blog post, we added points to our graphics. It helps identify the peaks of our names and highlights that the name associated with the line is the most popular in that specific interval in comparison with other names that are popular in later years.
  geom_point(aes(x = 1970 , y = .0448)) + # The value of the prop in 1970
  geom_point(aes(x = 1985 , y = .0337)) + # The value of the prop in 1985
  geom_point(aes(x = 2000 , y = .0165)) + # The value of the prop in 2000
  geom_point(aes(x = 2015 , y = .00963)) + # The value of the prop in 2015
  labs(title = "Do You Have a Hot Name, Baby?", subtitle = "Most Popular Male Names (1955-2015)", y = "Proportion of People", x = "Year", caption = "Source: babynames") + # Our (hopefully) interesting Title along with the axis-labels
  theme_update() # This theme was useful, in comparison with other themes, because it has vertical and horizontal lines-- this helps to get an idea of the inveral length and actually match up the points with a value on the y-axis
  



agg_f <- ggplot() + # Same with the plot above
  geom_line(data = mary , aes(x = year , y = prop , color = name) , size = 1) +
  geom_line(data = jennifer , aes(x = year, y = prop, color = name) , size = 1) +
  geom_line(data = jessica , aes(x = year, y = prop, color = name) , size = 1)+
  geom_line(data = emily , aes(x = year, y = prop, color = name) , size = 1) +
  geom_line(data = emma , aes(x = year, y = prop, color = name) , size = 1) +
  geom_point(aes(x = 1955 , y = .0315)) +
  geom_point(aes(x = 1970 , y = .0252)) +
  geom_point(aes(x = 1985 , y = .0262)) +
  geom_point(aes(x = 2000 , y = .0130)) +
  geom_point(aes(x = 2015 , y = .0105)) +
  labs(subtitle = "Most Popular Female Names (1955-2015)", y = "Proportion of People", x = "Year", caption = "Source: babynames") +
  theme_update()


grid.arrange(agg_m, agg_f, ncol = 1) # We used the gridExtra package here to arrange both of these graphics together without faceting by sex. If we faceted by sex, we would be unable to draw the points because it is hard to decipher which graph the points should go to.
```